
%Document generated using DScaffolding from https://www.mindmeister.com/1411994959
\documentclass{article}
\usepackage[utf8]{inputenc}

\newcommand{\todo}[1] {\iffalse #1 \fi} %Use \todo{} command for bringing ideas back to the mind map

\title{21EASE}
\author{}

\begin{document}

\maketitle
      

\section{Introduction}

%Describe the practice in which the problem addressed appears

    
%Describe the practical problem addressed, its significance and its causes
Research has shown that a major problem is that 1- An external, objective and effective assessment of Coding Reliability (SLR's data Validity) of completed (published) SLRs is difficult without having to audit them \cite{Petersen2015} \cite{Ali2019}. This problem is of particular concern as it is now well established that it can lead to B1.1-Produces loss of money \cite{Madeyski2018}, B2-Produces loss of CREDIBILITY \cite{Madeyski2018} \cite{Ampatzoglou2019} \cite{Madeyski2018}, B3-Produces loss of data \cite{Biffl2014} and B4.1-Not corrobarate published findings. Causes can be diverse: (1) A1.1.2-Reporting is an internal process made by SLR authors that leads to research bias, (2) A1.1.2-Peer reviewing is not the panacea, (3) A1.2-No information is provided in a SLR report \cite{Madeyski2018} \cite{Burda2016}, (4) A2.1.1-Guidelines and checklist only focus on reporting the process \cite{Burda2016} \cite{Burda2016}, (5) A2.1.2.1-Editorial or other restrictions (e.g. researchers want to continue publishing) \cite{Belur2018} \cite{Kitchenham2007} \cite{Biffl2014}, (6) A2.1.2.2.1-The coding (SLR) tool does not provide it and (7) A2.2-SLR data is not portable \cite{Al-Zubidy2017} \cite{Al-Zubidy2017}. 
    
%Summarise existing research including knowledge gaps and give an account for similar and/or alternative solutions to the problem
Existing research has tackled these causes. Ampatzoglou et al. addressed the A2.1.2.2.1-The coding (SLR) tool does not provide it \cite{Ampatzoglou2019}. Ali et al. addressed the A2.1.2.2.1-The coding (SLR) tool does not provide it \cite{Ali2019}. Petersen et al. addressed the A2.1.2.2.1-The coding (SLR) tool does not provide it \cite{Petersen2015}. Ali et al. addressed the A2.1.2.2.1-The coding (SLR) tool does not provide it \cite{Ali2019}. Ampatzoglou et al. addressed the A2.1.2.2.1-The coding (SLR) tool does not provide it \cite{Ampatzoglou2019}. Li et al. addressed the A2.2-SLR data is not portable \cite{Li2015}. 
    
%Formulate goals and present Kernel theories used as a basis for the artefact design
In this work, we address 3 main causes: A2.1-Raw data is not provided, A2.1.1-Guidelines and checklist only focus on reporting the process and A2.2-SLR data is not portable. 
    
%Describe the kind of artefact that is developed or evaluated
This article presents a novel artefact
    
%Formulate research questions

    
%Summarize the contributions and their significance

      
%Overview of the research strategies and methods used
This article has followed a Design Science Research approach.

%Describe the structure of the paper
The remainder of the paper is structured as follows: 

%Optional - illustrate the relevance and significance of the problem with an example
    
      
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
    